Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-07 paper/paper.Rmd
chase up remaining references

To understand the behaviour of the Forecast Hub ensembles we need to first explore the structure of the COVID-19 Forecast Hubs [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue].
These collaborations share a similar design with a central team running the hub, vetting forecasts, and producing the ensemble forecast as well as teams of independent forecast contributors who design their forecast models and then use them to produce a weekly forecast that they then submit to the central hub team. 
Each hub targets a range of metrics including test-positive reported cases, reported deaths, and hospitalisations has a specific geographic focus and asks for weekly forecasts (using epidemiological weeks i.e. Sunday to Saturday) over a time horizon of a few weeks.
Typically, the ensemble forecast produced each week comprises at least 3 independent forecasts using a range of approaches and is produced using an unweighted median ensemble [@Sherratt2022-ue].
Observed data are available and updated daily, and most submitted forecasts use this dataset, along with potentially other sources of real-time information, to produce forecasts.
Here, we focus on reported cases and primarily on the European Forecast Hub but our observations hold, in our view, across COVID-19 Forecast Hubs and to a lesser degree targets.
We focus on reported cases as these represent the most common forecast target for COVID-19 forecast models [@Nixon2022-zv], they are often of the most direct interest due to being a leading indicator, and they are generally the most challenging to predict.
In general, 5 main classes of forecast models are submitted [@Bracher2022-ug; @Cramer2022-sp], statistical forecasting models such as ARIMA models [@REF], mechanistic forecasting models based on the compartmental modelling framework and its generalisations [@REF], semi-mechanistic approaches that blend both of these approaches [@REF; @Bosse2022-hm], agent-based simulation models [@Rakowski2010-ft; @Adamik2020-if], and human insight based forecast models that may also include elements of other methods [@Bosse2022-hm].
Real-time evaluation has shown that each of these classes of models may perform well depending on the context and specific implementation of the forecast model [@Bosse2022-hm].

@@

Whilst we derived our surrogate model from a range of assumptions based on observing ensemble forecasts behaviour and the behaviour and structure of submitted models this was by no means as structured or complete a process as it could have been.
In follow-up work, a more rigorous approach to this could be taken to further refine this set of assumptions, in particular using the input of a wider pool of researchers. 
The findings from our study may also be useful for informing this improved set of assumptions. 
A particular focus should be on understanding why our surrogate model was liable to overestimate peak incidence and what simply additional assumptions may be used to mitigate this.
In addition, the model we derived based on our assumptions was likely not optimal both in terms of compute time and accuracy at reproducing ensemble-like behaviour.
Models with a more complex auto-correlation structure and more refined approaches to localised trends should be explored to improve relative performance to ensemble forecasts.
An example of a family of possible approaches are structural time series models which have many of the characteristics implied by our assumptions for how forecast ensembles typically operate.
As we identified that the tails of our predictive distributions were responsible for a large proportion of the difference in performance compared to the forecast ensemble it may be the case that post-processing of forecasts from our surrogate model would enhance their similarity to the forecast ensemble.
This seems likely to improve out-of-sample performance but does not help with the secondary aim of understanding the implicit assumptions driving the performance of multi-model, multi-team infectious disease forecast ensembles.
As we have hypothesised that the use of absolute scoring measures is inappropriate and leads to performance characteristics that are unlikely to be favoured by forecast stakeholders more work should be done in this area.
If new forecast ensemble methods are adopted as best practice by Forecast Hubs then follow-up work attempting to create surrogate forecast models should also use these approaches and this will likely alter the observed characteristics of the hub ensemble forecasts, for example, the tendency to be poorly calibrated.
In September 2022, GitHub announced support for hosted GitHub Action runners with additional compute power [@GitHubActionsLargeRunners]. Whilst a paid feature this may allow more compute-intensive models, with fewer potential performance trade-offs, to be easily democratised though only if funds are available to support the hosting costs.
One potential research area is to explore forecasting methods that can be used with a range of computing resources though this would require extensive evaluation and documentation to make it clear to users what the trade-offs between compute usage and forecast performance are.
More work is needed to understand the best practice treatment of data revisions when evaluating forecasts and the potential bias these may cause.
Lastly, here we have only explored a surrogate for an ensemble for a single disease, a limited set of locations, and a single target (incident cases), meaning our findings are difficult to generalise.
Follow-up work should explore whether this behaviour holds across diseases, locations, and epidemiological targets where the behaviour of ensembles is notably different [@REF].
However, this work is limited by the lack of large-scale forecast ensembling projects despite them showing obvious promise to improve the forecasts available to stakeholders.

>>>>

To understand the behaviour of the Forecast Hub ensembles we need to first explore the structure of the COVID-19 Forecast Hubs [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue].
These collaborations share a similar design with a central team running the hub, vetting forecasts, and producing the ensemble forecast as well as teams of independent forecast contributors who design their forecast models and then use them to produce a weekly forecast that they then submit to the central hub team. 
Each hub targets a range of metrics including test-positive reported cases, reported deaths, and hospitalisations has a specific geographic focus and asks for weekly forecasts (using epidemiological weeks i.e. Sunday to Saturday) over a time horizon of a few weeks.
Typically, the ensemble forecast produced each week comprises at least 3 independent forecasts using a range of approaches and is produced using an unweighted median ensemble [@Sherratt2022-ue].
Observed data are available and updated daily, and most submitted forecasts use this dataset, along with potentially other sources of real-time information, to produce forecasts.
Here, we focus on reported cases and primarily on the European Forecast Hub but our observations hold, in our view, across COVID-19 Forecast Hubs and to a lesser degree targets.
We focus on reported cases as these represent the most common forecast target for COVID-19 forecast models [@Nixon2022-zv], they are often of the most direct interest due to being a leading indicator, and they are generally the most challenging to predict.
In general, 5 main classes of forecast models are submitted [@Bracher2022-ug; @Cramer2022-sp], statistical forecasting models such as ARIMA models, mechanistic forecasting models based on the compartmental modelling framework and its generalisations [@Srivastava2020-qv; @Li2021-cj], semi-mechanistic approaches that blend both of these approaches [@Castro2021-lj; @Bosse2022-hm], agent-based simulation models [@Rakowski2010-jn; @Adamik2020-if], and human insight based forecast models that may also include elements of other methods [@Karlen2020-pt; @Bosse2022-hm].
Real-time evaluation has shown that each of these classes of models may perform well depending on the context and specific implementation of the forecast model [@Bosse2022-hm].

@@

Whilst we derived our surrogate model from a range of assumptions based on observing ensemble forecasts behaviour and the behaviour and structure of submitted models this was by no means as structured or complete a process as it could have been.
In follow-up work, a more rigorous approach to this could be taken to further refine this set of assumptions, in particular using the input of a wider pool of researchers. 
The findings from our study may also be useful for informing this improved set of assumptions. 
A particular focus should be on understanding why our surrogate model was liable to overestimate peak incidence and what simply additional assumptions may be used to mitigate this.
In addition, the model we derived based on our assumptions was likely not optimal both in terms of compute time and accuracy at reproducing ensemble-like behaviour.
Models with a more complex auto-correlation structure and more refined approaches to localised trends should be explored to improve relative performance to ensemble forecasts.
An example of a family of possible approaches are structural time series models which have many of the characteristics implied by our assumptions for how forecast ensembles typically operate.
As we identified that the tails of our predictive distributions were responsible for a large proportion of the difference in performance compared to the forecast ensemble it may be the case that post-processing of forecasts from our surrogate model would enhance their similarity to the forecast ensemble.
This seems likely to improve out-of-sample performance but does not help with the secondary aim of understanding the implicit assumptions driving the performance of multi-model, multi-team infectious disease forecast ensembles.
As we have hypothesised that the use of absolute scoring measures is inappropriate and leads to performance characteristics that are unlikely to be favoured by forecast stakeholders more work should be done in this area.
If new forecast ensemble methods are adopted as best practice by Forecast Hubs then follow-up work attempting to create surrogate forecast models should also use these approaches and this will likely alter the observed characteristics of the hub ensemble forecasts, for example, the tendency to be poorly calibrated.
In September 2022, GitHub announced support for hosted GitHub Action runners with additional compute power [@GitHubActionsLargeRunners]. Whilst a paid feature this may allow more compute-intensive models, with fewer potential performance trade-offs, to be easily democratised though only if funds are available to support the hosting costs.
One potential research area is to explore forecasting methods that can be used with a range of computing resources though this would require extensive evaluation and documentation to make it clear to users what the trade-offs between compute usage and forecast performance are.
More work is needed to understand the best practice treatment of data revisions when evaluating forecasts and the potential bias these may cause.
Lastly, here we have only explored a surrogate for an ensemble for a single disease, a limited set of locations, and a single target (incident cases), meaning our findings are difficult to generalise.
Follow-up work should explore whether this behaviour holds across diseases, locations, and epidemiological targets where the behaviour of ensembles is notably different.
However, this work is limited by the lack of large-scale forecast ensembling projects despite them showing obvious promise to improve the forecasts available to stakeholders.
